save

### 2024-03-27 qmd/save.qmd
updated locoweed report files

@@

>>>>

# row of images
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery-container {
      display: flex;
      justify-content: center;
      width: 100%;
    }
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(150px, 1fr));
      grid-gap: 10px;
      max-width: 1200px;
      width: 100%;
    }
    .gallery .gallery-img {
      width: 100%;
      min-wdth: 100px;
      object-fit: cover;
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .gallery .gallery-img:hover {
      transform: scale(1.05);
    }
    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8);
      display: none;
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }
    .expanded {
      max-width: 80%;
      max-height: 80%;
      cursor: pointer;
    }
    p.gallery-caption {
      text-align: center;
      font-style: italic;
      color: #8B8989;
    }
  </style>
</head>
<body>

<div class="gallery">
  <img src="locoweed/img/bombus-loco.jpg" alt="Image 1" class="gallery-img" onclick="expandImage(this)">
  <img src="locoweed/img/loco-bug.jpg" alt="Image 1" class="gallery-img" onclick="expandImage(this)">
  <img src="locoweed/img/field-loco1.jpg" alt="Image 1" class="gallery-img" onclick="expandImage(this)">
  <img src="locoweed/img/ghloco1-sq.jpg" alt="Image 1" class="gallery-img" onclick="expandImage(this)">
  <img src="locoweed/img/ghloco2-sq.jpg" alt="Image 1" class="gallery-img" onclick="expandImage(this)">
  <img src="locoweed/img/ghloco3-sq.jpg" alt="Image 1" class="gallery-img" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

<script>
  var currentImageIndex = 0;
  var galleryImages = document.querySelectorAll('.gallery-img');

  function expandImage(img) {
    currentImageIndex = Array.from(galleryImages).indexOf(img);
    document.getElementById('expanded-image').src = img.src;
    document.querySelector('.expanded-container').style.display = 'flex';
  }

  function closeExpanded() {
    document.querySelector('.expanded-container').style.display = 'none';
  }

  function navigateGallery(event) {
    var clickX = event.pageX - event.target.getBoundingClientRect().left;
    var imageWidth = event.target.offsetWidth;

    if (clickX < imageWidth / 2) {
      currentImageIndex = (currentImageIndex - 1 + galleryImages.length) % galleryImages.length;
    } else {
      currentImageIndex = (currentImageIndex + 1) % galleryImages.length;
    }

    document.getElementById('expanded-image').src = galleryImages[currentImageIndex].src;
  }
</script>

</body>
</html>

@@

# two images cenetered on the screen
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>Centered Images</title>
    <style>
        .image-container {
            display: flex;
            align-items: center;
            justify-content: center;
        }

        .image-container img {
            max-width: 150px; /* Adjust image size as needed */
            height: auto;
            margin: 0 150px; /* Add space between the images */
        }
    </style>
    </head>
    <body>

    <div class="image-container">
        <img src="locoweed/img/field-loco1.jpg" alt="Image 1">
        <img src="locoweed/img/bombus-loco.jpg" alt="Image 2">
    </div>

</body>
</html>
```
